%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{ #1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-15pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://taichikato.com/}{\Large Taichi Kato}} & Email : \href{mailto:tkato24@amherst.edu}{tkato24@amherst.edu}\\
  \href{http://taichikato.com/}{http://taichikato.com} & Mobile : +‭1-413-‭‭2754-569 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amherst College}{Amherst, MA}
      {Bachelor of Art in Computer Science and Mathematics}{Expected: May. 2024}
       \resumeItemListStart
	      \resumeItem{\textbf{Honours}: Davis UWC Scholar}
      \resumeItemListEnd
      \vspace{5pt}
    \resumeSubheading
      {United World College of South East Asia}{Singapore}
      {International Baccalaureate Diploma, 98th Percentile (43/45)}{Aug. 2013 -- May. 2020}
      \resumeItemListStart
      	  \resumeItem{\textbf{Relevant Coursework}: HL Mathematics, HL Computer Science, HL Physics, SL Philosophy}
	      \resumeItem{\textbf{Honours}: Bilingual Diploma in Japanese and English}
	      \resumeItem{\textbf{Thesis}: \textit{Evaluating Marx and Nietzsche's ideas of entfremdung and ressentiment in the context of increased technological automation (Philosophy and Computer Science)}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Questo AI}{Singapore}
      {Co-Founder and Software Engineer}{Nov. 2016 - Aug. 2020} % Date(s)
      \resumeItemListStart
        \resumeItem {\textbf{Built} a service that generates quizzes from learning materials}
        \resumeItem {\textbf{Pitched} to investors, and was granted \textbf{\$160,000} in subsidised funding from Google and IBM.}
        \resumeItem {\textbf{Led} a team of three for an organic marketing campaign, attaining \textbf{8,000 downloads} from ProductHunt(\#1, 140+ upvotes) and HackerNews(500+, \#1 Product of the Day)}
        \resumeItem {\textbf{Researched and developed} a novel question generation algorithm modifying a neural translation model, collaborating with two other engineers, using \textbf{Numpy, Pandas, Tensorflow, and PyTorch}. Shipped to production as micro services using \textbf{Python, Flask and Google Cloud}. Developed our deployment pipeline using \textbf{Docker, Kubernetes, and Travis CI}.}
        \resumeItem {\textbf{Designed and developed} the iOS application using Swift and CoreML}
         \resumeItem{\textbf{Designed and developed} machine learning solutions for consulting clients, generating \textbf{\$56,000} in revenue.}
        \resumeItem {\textbf{Awarded} the Overall Winner Student Category @ IBM PitchIT 2016.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
	\resumeSubheading
	{University of Tsukuba, Digital Nature Group} % Organization
    {Tsukuba, Japan} % Location
    {Deep Learning Researcher Intern} % Job title
    {Jul. 2018 – Aug. 2018} % Date(s)
    \resumeItemListStart
        \resumeItem {\textbf{Researched} 2D to 3D extrapolation with GANs under direct mentorship of Prof. Ochyai Yoichi. \textbf{Presented} a poster on the research.}
        \resumeItem {Conducted literature review of GANs, and presented the findings using \textbf{Powerpoint}}
      \resumeItemListEnd
\resumeSubHeadingListEnd
\resumeSubHeadingListStart
	\resumeSubheading
    {Mercari, Inc.} % Organization
    {Tokyo, Japan} % Location
    {Machine Learning Engineer Intern} % Job title
    {Jun. 2018 - Jul. 2018} % Date(s)
    \resumeItemListStart
        \resumeItem {Collaborated with senior engineers and researchers to introduce edge computing to the pipeline.}
        \resumeItem {\textbf{Minimized the size} of price prediction and object detection models \textbf{by 70\%} using \textbf{PyTorch and Tensorflow} through quantization and pruning, allowing them to run on mobile devices without sacrificing accuracy.  \textbf{Reduced the cost }required to process listings from \textbf{16 million monthly active users}}
        \resumeItem {Rapidly \textbf{iterated on, and developed} an iOS prototype which gives price predictions of objects in the camera feed in real time. Youngest employee ever at 16 years old.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
\resumeSubHeadingListStart
	\resumeSubheading
	{teamLab, Inc.} % Organization
    {Tokyo, Japan} % Location
    {Software Engineer Intern} % Job title
    {Jun. 2017 – Jul. 2017} % Date(s)
    \resumeItemListStart
        \resumeItem {\textbf{Initiated and led} the development of an internal Redux framework for iOS, which has been used extensively in company's future projects, {collaborated} with designers, business development, and back-end engineers on developing an iOS applications using \textbf{Swift}. Youngest employee ever at 15 years old.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXTRA CURRICULARS-----------------
\section{Activities}
  \resumeSubHeadingListStart
  	\resumeSubItem{\textbf{Amherst College (2020 - Present)}: Member of the Rowing team, Computer Science Club, Computer Intelligence Lab, Quantitative Trading Club, Investment Club, Philosophy Club, and Asian Students Association}
  	  \resumeSubItem{\textbf{Lead Organiser of YouthHacks (2017-2019)}: Organised Singapore's largest pre-university hackathon. Raised over \textbf{\$5,000 } for \textbf{180 participants}, from sponsors ranging from National Youth Council, Google, StartupX, and Reactor School. Reached out to mentors, judges and participants through organic marketing; Organised logistics and financing for the event. Held seminars on UI design and on utilising machine learning in hackathons.}
  	 \resumeSubItem{\textbf{President of UWCSEA Hack Club (2017-2020)}: Taught 30+ computer science students in high school, teaching Python, Javascript, and gave seminars on introduction to machine learning.}
  	   	 \resumeSubItem{\textbf{President of UWCSEA Photography Club (2018-2020)}: Instructed 20+ young students about fundamentals of photography and photo editing.}
	\resumeSubHeadingListEnd 



%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  	\resumeSubItem{\textbf{Zipcall (2020)}: Developed multi-client decentralised video-calling service. \textbf{100,000 MAU}.}
	\resumeSubItem{\textbf{Kafka NLP (2020)}: Developed the first-ever open-source implementation of dependency parsing on iOS}
	\resumeSubItem{\textbf{Bookworm (2019)}: Awarded the Best Pre-University Hack Prize@NUS Hack'n'Roll (331 hackers). Built a dictionary app which makes physical books interactive, using \textbf{OpenCV and React Native}}
	\resumeSubItem{\textbf{Photonify (2017)}: \textbf{Awarded \$30,000} for Most Creative@SWSG2017 – (550+ hackers). Built an app that analyses image composition, and displays real time guidance to improve mobile photography.} 
	\resumeSubItem{\textbf{Hequals (2017)}: \textbf{Awarded \$500} for Pre-University Overall Winning Team @\#codeathon 2017 (73 participating teams). Built a service that assigns GitHub tasks to people in a team based on previous commits, made to reduce bias in tech.} 
	\resumeSubHeadingListEnd 

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
